\plaintitle

### 2017-01-06 drafts/labor/piecework_lit.tex

\topic{By \citeyear{hughRaynbirdTaskWork} we find
a concise definition of piecework
in \citeauthor{hughRaynbirdTaskWork}'s essay
(where he also calls piecework ``measure work'', ``grate work'', and ``task work''),
particularly driven toward encapsulating the manual labor of farmwork.}
\citeauthor{hughRaynbirdTaskWork} does this by contrasting with the ``day--labourer'' ---
``the chief difference lies between the day--labourer,
who receives a certain some of money~\dots~for his day's work,
and the task--labourer, whose earnings depend on the quantity of work done''~\cite{hughRaynbirdTaskWork}.
\citeauthor{10.2307/2338394} defines it through examples:
``payment is made for each hectare which is pronounced to be well ploughed~\dots~for each living foal got from a mare;~\dots~for each living calf got''~\cite{10.2307/2338394}.
This framing offers a more intuitive sense;
``payment for results,'' as he calls it,
is not only common in practice, but
well--studied in labor economics as well~\cite{Figlio2007901,weitzman1976new,10.2307/3003414,BJIR:BJIR038}.

@@

\topic{Piecework's popularity in the United States and Europe plummeted almost as quickly as it had climbed.}
Between 1938 and 1942, piecework in a number of metal workers had climbed as steeply as from 11\% to 60\%~\cite{hart2005piecework};
by 1961, that proportion dropped to as little as 8\%~\cite{carlson1982time}.
\citeauthor{carlson1982time} details that, from 1973 to 1980, the remaining bastions piecework
--- where more than 50\% worked under incentive wage plans ---
were principally in clothes--making (e.g. hosiery, footwear, and garments).
\citeauthor{hart2013rise}'s work substantively explores the precipitous decline of piecework in the last third of the \nth{20} century.

@@

@@

% \topic{When piecework entered the American economy, it was not used for complex work.}
% One reason for low complexity was workers' skills:
% it was infeasible to provide new pieceworkers with the comprehensive education
% that apprenticeships imparted~\cite{hart2013rise}.
% So, initially piecework in the United States arose for farm work, and as
% \citeauthor{hughRaynbirdTaskWork} and others discuss,
% the practice remained relatively obscure until
% it blossomed in the textile industry~\cite{hughRaynbirdTaskWork}.
% \msb{this is not about domestic/farmhand labor...might need to move up or be cut...or is it? clarify that this is domestic labor moving into NYC?}
% The complexity of the work remained low at the turn of
% the \nth{20} century as piecework saturated New York City~\cite{riisOtherSideLives}.
% \msb{how is this sentence relevant to the case study?:}
% However, writers of the time focused their attention on
% wage~\cite{burton1899commercial} and
% management regimes~\cite{norton1900textile}
% rather than training.
% Mass manufacturing,
% such as sewing garments~\cite{riisOtherSideLives} and making matchsticks~\cite{10.2307/3827491},
% flourished under piecework systems in densely populated cities.

% \topic{Workers' relationships with employers quickly soured.}
% \msb{We haven't met the match--girls yet. Is this case study supposed to be about them? They come out of nowhere, and we're talking about their strike rather than them.}
% The match--girls strike of 1888 was one of the earliest and most famous successful worker strikes,
% and perhaps the beginning of ``militant trade unionism''~\cite{10.2307/3827491}.
% As \citeauthor{weyer1894history} described,
% ``the match--girls' victory turned a new leaf in Trade Union annals''~\cite{weyer1894history}: in the 30 years after the match--girls strike,
% the Trade Union Movement enrollment grew from 20\% of eligible workers to over 60\%.

% \topic{The match--girls strike foreshadowed both collective action victories and an emerging paradigm regarding worker management.}
% \msb{this paragraph seems to be about collective action rather than domestic/farmhand labor. also, coal miners aren't domestic or farmhand.}
% Coal miners won a nationwide individual minimum wage after The Great Coal Strike of 1912~\cite{10.2307/2221944}.
% Garment workers in Philadelphia secured collective bargaining rights in 1915 after a prolonged strike and threat of a second~\cite{10.2307/41829256}.
% \msb{Why is Taylor relevant to this case study?}
% \ali{I'm just clumsily interleaving the contemporary literature with the events.
% I'd like to say ``This is the geist of work in their time'';
% is this a bad idea?}
% It was in the midst of this time that \citeauthor{taylor1914principles} published
% the work for which he would later be called ``the father of scientific management''~\cite{RePEc:mtp:titles:0262612062}.
% It was this framing on work \& worker management that gave workers a concrete adversary
% --- if not Taylor, then \textit{Taylorism}  ---
% against which to rally~\cite{jacoby1983union,parker1920casual}.

>>>>

\topic{By \citeyear{hughRaynbirdTaskWork} we find
a concise definition of piecework
in \citeauthor{hughRaynbirdTaskWork}'s essay on piecework
(where he also calls it ``measure work'', ``grate work'', and ``task work''),
particularly driven toward encapsulating the manual labor of farmwork.}
\ali{I just made the line ``Raynbird's essay on piecework''; is that enough to make it sound less important?}
\citeauthor{hughRaynbirdTaskWork} does this by contrasting with the ``day--labourer'' ---
``the chief difference lies between the day--labourer,
who receives a certain some of money~\dots~for his day's work,
and the task--labourer, whose earnings depend on the quantity of work done''~\cite{hughRaynbirdTaskWork}.
\citeauthor{10.2307/2338394} defines it through examples:
``payment is made for each hectare which is pronounced to be well ploughed~\dots~for each living foal got from a mare;~\dots~for each living calf got''~\cite{10.2307/2338394}.
This framing offers an intuitive sense of piecework;
``payment for results,'' as he calls it,
is not only common in practice, but
well--studied in labor economics as well~\cite{Figlio2007901,weitzman1976new,10.2307/3003414,BJIR:BJIR038}.

@@

\topic{Piecework's popularity in the United States and Europe plummeted almost as quickly as it had climbed.}
Between 1938 and 1942, the proportion of metal workers who were pieceworkers had climbed steeply 11\% to 60\%~\cite{hart2005piecework};
by 1961, that proportion dropped to as little as 8\%~\cite{carlson1982time}.
\citeauthor{carlson1982time} details that, from 1973 to 1980, the remaining bastions of piecework
--- where more than 50\% worked under incentive wage plans ---
were principally in clothes--making (e.g. hosiery, footwear, and garments).
\citeauthor{hart2013rise}'s work substantively explores the precipitous decline of piecework in the last third of the \nth{20} century.

@@

\msb{If you want to make the argument in the last paragraph of this subsection that piecework assumed no professional skills, it's worth calling that out slightly more visibly throughout the subsection.}\ali{I don't want to suggest that, actually, at least not ultimately; in the beginning, sure, but by WWII it definitely required certain specialized training (arguably in Airy's case too)}

@@
